---
title: "Ranking Prediction for NBA Players"
author: "PSTAT 131/231 Teo Zeng"
output:
    html_document:
      toc: true
      toc_float: true
      code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warning = FALSE)
```

## NBA Players Ratings Prediction

```{r}
library(ggplot2)
library(tidyverse)
library(tidymodels)
library(corrplot)
library(ggthemes)
library(yardstick)
tidymodels_prefer()

setwd("~/Desktop/PSTAT 131/pstat131-project")
set.seed(125)
```

### An Overview of Dataset

The dataset is downloaded as a csv file and is obtained from a [kaggle dataset by William Yu](https://www.kaggle.com/datasets/willyiamyu/nba-2k-ratings-with-real-nba-stats). 

```{r}
ratings <- read.csv(file = 'data/nba_rankings_2014-2020.csv')
summary(ratings)
```

As we can see from the summary statistics, there are a total of 2412 observations, and there are a total of 29 predictors. The variables I will be working with are all numbers, while some are strings. So far, there  is no missing data and the dataset is considered complete.

### An Overview of Your Research Questions

For this dataset, we are interested in predicting the "rankings" variable, which reflects the ratings of each NBA Players. The minimum is 62 and and the maximum is 98 with a mean of 75.66. I think predictors like age, points per game, field goal, plus minus would be helpful in predicting a player's ratings, since, in general, these factors should be positively related.

The goal of this model is predictive.

### Proposed Project Timeline

I think I will begin exploratory data analysis at the beginning of next week, and complete one model per week.

### Questions and Concerns 

For now there is no.